Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-16 paper.tex
Add two paragraphs discussing performance

\todo[inline]{Discuss drag coefficient curves.}

@@

Mean power and drag coefficients at $\lambda=1.9$ are plotted in
Figure~\ref{fig:perf-Re-dep}

>>>>

@@

Mean power and drag coefficients at $\lambda=1.9$ are plotted for all Reynolds
numbers in Figure~\ref{fig:perf-Re-dep}. There is a drastic improvement in $C_P$
with increasing Reynolds number for the lower values. Power coefficient then
becomes  essentially $Re$-independent at $Re_D = 0.8 \times 10^6$, which
corresponds to an approximate average blade chord Reynolds number $Re_{c,
\mathrm{ave}} = 2.1 \times 10^5$. This threshold is consistent with the behavior
of the blade boundary layer transitioning from laminar to turbulent, thereby
promoting reattachment of the laminar separation bubble.

The behavior of the mean rotor drag coefficient is similar, though the changes
are less dramatic. This is likely due to cross-flow turbine geometry, where
increases in blade drag at lower $Re$ somewhat offset the reduction in lift, to
keep total streamwise force from changing as much as the rotor torque. The
tendency for $C_D$ to continue increasing with $Re$ may also be a consequence of
increasing Froude number, which therefore increases free surface deformation and
wave drag during towing without increasing flow through the turbine.
